### 2014-04-24 Docs/compilers/compilers.tex
Added notes on the multifab_volume() error and made minor fixes to the incomp_shear_jet test problem.
Edison note

 A separate issue is that the ``volume'' reported by {\tt
 multifab\_volume()} seems to be wrong.  For a single level run, it
 should just be $\mathtt{nx} \times \mathtt{ny} \times \mathtt{nz}$,
 but the value reported is incorrect.
\end{itemize}

>>>>

 A separate issue is that the ``volume'' reported by {\tt
 multifab\_volume()} seems to be wrong.  For a single level run, it
 should just be $\mathtt{nx} \times \mathtt{ny} \times \mathtt{nz}$,
 but the value reported is incorrect.  This issue only manifests when
 using OpenMP, so it is likely related to the OpenMP loop in {\tt
 boxarray\_volume()}, which is called by \code{multifab\_volume()}.
 In Cray 8.2.4 the problem appears to be resolved, with  
 \code{\tt multifab\_volume()} returning the correct cell count.

\item Cray 8.2.6 on NERSC Edison seems to work well with OpenMP.
